visualFields 1.0.7: Tools for Analyzing the Field of Vision in \proglang{R}

### 2025-05-19 jss-article-rnw/article.Rnw
Modified sensitivity scale.

At the conclusion of the test, the inverse of the contrast threshold, $\Delta L_{threshold}$, is recorded at each location using a logarithmic decibel (dB) scale. This scale is defined as the attenuation from the maximum possible stimulus contrast, $\Delta L_{max}$:

\begin{equation}
dB = -10\ \rm log \left (\frac{\Delta L_{\rm thr}}{\Delta L_{\rm max}} \right)\ .
\end{equation}

For common devices such as the Humphrey Field Analyzer and the Octopus 900, the maximum luminance differential is $\Delta L_{max} = \frac{10{,}000\ apostilbs}{\pi} \approx 3183.1\ cd,{m}^{-2}$.

>>>>

At the conclusion of the test, the perimetric sensitivity is recorded in a logarithmic decibel (dB) scale based on the luminance of the stimulus at threshold ($L_{threshold}$). In perimetry, luminance is usually reported in apostilbs rather than $cd/m^2$, where $1 asb = \frac{1}{\pi} cd/m^2$. This scale is defined as the attenuation from the maximum possible stimulus contrast, $L_{max}$:

\begin{equation}
dB = 10\ \rm log \left (\frac{L_{\rm max}}{L_{\rm threshold}} \right)\ .
\end{equation}

$L_{max}$ may differ between parameter types, and the Humphrey Field Analyzer uses 10,000 asb, whereas recent Octopus 900 perimeters commonly use 4000 asb.
